Robust Agglomeration of Labeled Neurons using 3D Skeletonization

### 2017-11-06 papers/cvpr2018/1_related_work.tex
paper: updated evaluation and results

\paragraph{Graph-based methods}. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
This closely resembles the biological constraint that neurons have a topological genus of zero. 
There are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}

>>>>

\paragraph{Graph-based methods.} Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}. 
The multicut graph partitioning algorithm extracts segments the graph and remove edges such that there are no cycles. 
This closely resembles the biological constraint that neurons have a topological genus of zero. 
There are several useful multicut heuristics which provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,kernighan1970efficient,keuper2015efficient}

### 2017-11-06 papers/cvpr2018/3_evaluation.tex
paper: updated evaluation and results

We evaluate our proposed methods on two different connectomics datasets from two different species.

@@

\subsubsection{Kasthuri}

@@

@@

@@

HOW DO WE EVALUATE THE PRUNING METHOD
HOW MANY EXAMPLES DO WE MISS

@@

HOW DO WE TRAIN THE CLASSIFIER - split the data in half and have training and validation
DATA AUGMENTATION
HOW MANY LEARNABLE PARAMETERS
WHAT NETWORKS DID WE TRY
HAVE A TABLE WITH PARAMETERS: ITERATIONS, momentum, batch size, learning rate

@@

>>>>

We evaluate our proposed methods on two different connectomics datasets, one anisotropic and the other isotropic, from two different species.

@@

\subsubsection{Kasthuri}
The Kasthuri dataset images the neocortex of a mouse brain produced by a scanning electron microscope \cite{kasthuri2015saturated}. 
This dataset is $338 \times 3618 \times  5342$ voxels in size. 
The resolution of the dataset is $3 \times 3 \times 30 \textrm{nm}^3$. 
We evaluate our methods using the left cylinder of this 3-cylinder dataset.

@@

The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy.  
The mushroom body is this species is the major site of associative learning \cite{takemura2017connectome}. 
The original dataset contains a $40 \mu\textrm{m} \times 50\mu\textrm{m} \times 120\mu\textrm{m}$ volume of which we use two subsections of size $1000 \times 1000 \times 1000$ voxels.  
The resolution of this dataset is $10 \times 10 \times 10 \mu\textrm{m}^3$ per voxel. 
The image data and the accompanying ground truth is available (CITE).

@@

Our algorithm takes the output of a supervoxel based agglomeration strategy such as NeuroProof or GALA. For our experiments we use the output from NeuroProof (CITE). We generate voxel affinities from the raw image data using the U-Net architecture \cite{ronneberger2015u}. The Zwatershed algorithm (CITE) creates an oversegmentation of the neurons given these voxel affinities. We input the raw image data, the voxel affinities, and the oversegmentation into NeuroProof which performs a hierarchical agglomeration strategy to merge the supervoxels into larger and larger segments. Two neighboring segments receive a merge-likelihood score based on various extracted features such as the distribution of affinities along the segment boundary. A random forest classifier generates probabilities based on these features. (TODO: TOUFIQ ADD HERE)

@@

Our method prunes potential merge candidates by considering the skeleton as a simplification of the segment shape. Segment skeletons that have nearby endpoints are merge candidates. The underlying assumption in this model is that the segments break in a particular fashion, primarily perpendicular to the direction of travel (CONFUSING). We perform a series of experiments to evaluate the effectiveness of this idea. First, we examine how many merge candidates are not considered using our method that would have been if we employed the strategy of considering all neighboring segments. These are locations that we cannot possibly correct and therefore we want this number to be as low as possible. The second experiment considers how many locations are not considered that should not be merged. We want this number to be as large as possible since we want to avoid making mistakes by merging these segments. At best, these segments waste time and at worst they lead to incorrect merges.

@@

We divide both datasets into half to train the classifier. We generate all valid examples for merge consideration based on the skeletonization algorithm. In the training dataset, $80\%$ of the examples are used for training and the remaining examples are used for validation. To start, we consider networks of varying sizes, optimization functions, and loss functions. The supplemental material has additional information concerning the tuning of the network. There are XXX,XXX learnable parameters in our final architecture. The training ran for XX epochs. Table \ref{table:architecture} provides the final network parameters.

\begin{table}[h!]
	\centering
	\begin{tabular}{l l} \hline
		\textbf{Parameters} & \textbf{Values} \\ \hline
		Loss Function & Mean Squared Error \\
		Optimizer & SGD  with Nesterov Momentum \\
		Momentum & 0.9 \\
		Initial Learning Rate & 0.01 \\
		Decay Rate & $5 * 10^{-8}$ \\
		Activation & LeakyReLU $(\alpha = 0.001)$ \\
		Kernel Sizes & $3 \times 3 \times 3$ \\
		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
	\end{tabular}
	\caption{The parameters for the trained neural network.}
	\label{table:architecture}
\end{table}

\paragraph{Data Augmentation.}
We apply some data augmentation to the generated examples to increase the size of the training datasets. 
We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirrors along the $x$ and $z$ axes. 
This produces an additional 16 times more training data.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{./figures/multicut.png}
	\caption{An example of the benefits of using multicut over simpler agglomeration schemes. If we input this example into a na\"ive agglomeration strategy that collapses all edges with a threshold greater than 0.5, this entire segment will merge together despite the fact that nodes 2 and 4 and nodes 3 and 5 have low affinities.}
	\label{fig:multicut}
\end{figure}

Most current agglomeration strategies in connectomics consider all pairs of neighboring segments. A classifier produces a probability that each pair belongs to the same segment. All segment pairs with a probability above a certain threshold are merged together. Consider the simple example in Figure \ref{fig:multicut}. Under the existing agglomeration schemes this entire graph would become one segment. However multicut eliminates all cycles within the graph creating two unique segments. We compare our results using both the traditional hierarchical agglomeration strategy with the graph-based approach we propose.

\subsection{Variation of Information}

We use the variation of information metric to determine the accuracy of our pipeline. The variation of information measures the distance between two segmentations and is similar to mutual information. A lower variation of information score corresponds to a segmentation closer to the ground truth. (TODO: TOUFIQ ADD HERE)

### 2017-11-06 papers/cvpr2018/4_results.tex
paper: updated evaluation and results

\subsubsection{Finding Merge Candidates}

\subsubsection{Finding Split Candidates}

Effective pruning for merge candidates should have high precision and recall for segments that should be merged.

\subsection{Neural Network Classification}

\subsubsection{Merge Network}

\begin{figure}
	\includegraphics[width=0.85\linewidth]{figures/skeleton-training-curve.png}
	\caption{The training and validation loss when training the neural network on the L. Cylinder data set.}
	\label{fig:training-curve}
\end{figure}

\begin{figure}
	\includegraphics[width=0.85\linewidth]{figures/roc-microns-300-test.png}
	\caption{The ROC curve for the training and validation datasets.}
	\label{fig:roc-curve}
\end{figure}

Figure \ref{fig:training-curve} shows the training and validation loss during the training of the neural network.

\begin{figure*}[t]
	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-train.png}
	\hspace{0.0825\linewidth}
	\includegraphics[width=0.45\linewidth]{figures/variation_of_information-test.png}	
\end{figure*}

\subsubsection{Split Network}

\subsection{Graph-based Error Correction}

>>>>

\paragraph{Finding Positive Examples.}

As a baseline, we consider all pairs of segments that have neighboring voxels and see what percent of these segments are considered for merging. In the L. Cylinder dataset, there are XXX neighboring segments which have at least adjacent voxels. Our method which uses skeletons to prune the considered candidates finds XXX of these segments, or XX\% percent. On the FlyEM dataset, there are XXX adjacent segments with XXX found (XX\% percent). Figure \ref{fig:skeleton-results} shows some of the missed examples. The most common errors are the dendrite spines where the larger segment did not have an endpoint near the split. However, our algorithm does not require segments to be adjacent to merge. This offers a great benefit compared to traditional methods. In our datasets XXX and XXX segments are candidates for merging despite not having adjacent voxels. Figure \ref{fig:skeleton-results} gives one such pair which is merged given the results of our algorithm.

\paragraph{Pruning Negative Examples.}

Traditional agglomeration strategies consider a large number of negative candidates that we hope to prune. The original approach of considering adjacent supervoxels has XX,XXX and XX,XXX candidates which do not belong to the same neuron. With our pruning algorithm, this reduces to X,XXX and X,XXX, a factor of over XX times. This allows a more reasonable training environment with greater balance between the positive and negative merge examples.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate1.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/merge_candidate2.png}
	\caption{Two erroneously split segments that should merge together. Most segments that we want to merge have the same general structure.}
	\label{fig:skeleton-results}
\end{figure}

\subsection{Classification Performance}

Table \ref{table:classification} shows the precision and recall for all of the datasets. Our methods are more general than traditional connectomics examples allowing us to train the network on an anisotropic dataset and get impressive results on an isotropic dataset. Our initial network does not take in any image data, only the segment shapes, so we merely extract the $1200 \textrm{nm}^3$ region from any dataset and rescale as input into the neural network. For each of the tables, the top left square gives the number of segments which should merge that we predict merge. The bottom right square gives the number of segments which should not merge that we predict should not merge. The bottom left quadrant indicates the amount of false positives, candidates which we predict merge which do not. The top right quadrant gives the amount of false negatives where we predict split although the candidates should merge. Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

\begin{figure}
	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
	\caption{The receiver operating characteristic (ROC) curve for all four datasets.}
	\label{fig:network-results}
\end{figure}

\subsection{Graph Based Strategies}

Using a graph-based optimization strategy prevents XX segments from merging compared to the simple hierarchical agglomeration strategy with an optimal threshold cut off. Since correcting merge errors is significantly more difficult than correcting split errors, it is desirable to limit the number of false merges. The graph-based strategies significantly improve this error type.

\subsection{Variation of Information Improvements}

The final metric for comparing two connectomics segmentations is computing the variation of information with respect to an expert-labeled ground truth dataset. Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue).

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-train.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-test.png}
	\caption{The improvement on variation of information from the baseline NeuroProof segmentation (green). Results closer to the origin are better.}
	\label{fig:variation-of-information}
\end{figure*}
